---
output: github_document
---

[Link](https://github.com/elbersb/tidylog) to where the original R package came from.

[Deployed website](https://jhu-statprogramming-fall-2022.github.io/biostat840-project3-pkgdown-sparthib/) that you will do in Part 1E.

#### 5 things customized:

1.  Background color

2.  Foreground color

3.  Primary Color

4.  Navigation bar structure

5.  Home sidebar structure

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tidylog

[![CRAN Version](https://www.r-pkg.org/badges/version/tidylog)](https://CRAN.R-project.org/package=tidylog) [![Downloads](http://cranlogs.r-pkg.org/badges/tidylog)](https://CRAN.R-project.org/package=tidylog) [![R-CMD-check](https://github.com/elbersb/tidylog/workflows/R-CMD-check/badge.svg)](https://github.com/elbersb/tidylog/actions) [![Coverage status](https://codecov.io/gh/elbersb/tidylog/branch/master/graph/badge.svg)](https://codecov.io/github/elbersb/tidylog?branch=master)

The goal of tidylog is to provide feedback about dplyr and tidyr operations. It provides simple wrapper functions for almost all dplyr and tidyr functions, such as `filter`, `mutate`, `select`, `full_join`, and `group_by`.

## Example

Load `tidylog` after `dplyr` and/or `tidyr`:

```{r message=FALSE, warning=FALSE}
library("dplyr")
library("tidyr")
library("tidylog", warn.conflicts = FALSE)
```

Tidylog will give you feedback, for instance when filtering a data frame or adding a new variable:

```{r}
filtered <- filter(mtcars, cyl == 4)
mutated <- mutate(mtcars, new_var = wt ** 2)
```

Tidylog reports detailed information for joins:

```{r}
joined <- left_join(nycflights13::flights, nycflights13::weather,
    by = c("year", "month", "day", "origin", "hour", "time_hour"))
```

In this case, we see that 1,556 rows from the `flights` dataset do not have weather information.

Tidylog can be especially helpful in longer pipes:

```{r}
summary <- mtcars %>%
    select(mpg, cyl, hp, am) %>%
    filter(mpg > 15) %>%
    mutate(mpg_round = round(mpg)) %>%
    group_by(cyl, mpg_round, am) %>%
    tally() %>%
    filter(n >= 1)
```

Here, it might have been accidental that the last `filter` command had no effect.

## Installation

Download from CRAN:

``` r
install.packages("tidylog")
```

Or install the development version:

``` r
devtools::install_github("elbersb/tidylog")
```
